Quantifying the home ground advantage

### 2020-03-19 inst/home_advantage.Rmd
explicitly name rownames and colnames

teams <- LETTERS[1:4]
rownames(home_games_won) <- teams
colnames(home_games_won) <- teams
rownames(away_games_won) <- teams
colnames(away_games_won) <- teams

>>>>

teams <- LETTERS[1:4]
dimnames(home_games_won) <- list("@home" = teams,"@away"=teams)
dimnames(away_games_won) <- list("@home" = teams,"@away"=teams)
